Diffusive Homeostasis in a Self-Organizing Recurrent Neural Network \\ \begin{large} Spatially Dependent Interaction As a Determinant of Neural Activity and Plasticity \end{large}

### 2017-03-20 draft_duplex_shift_half_cm.tex
.

\documentclass[10pt,a4paper]{article}
%\usepackage{layouts}
\usepackage[a4paper,margin=1.5in]{geometry}
%\usepackage{geometry}
%\geometry{
%a4paper,
%left=2.0in,
%right=1.0in}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{tabu}
\usepackage{float}
\usepackage{upgreek}
\usepackage[titletoc,title]{appendix}
\usepackage{afterpage}
\usepackage[nottoc,notlot,notlof]{tocbibind}

@@

\pagenumbering{gobble}

@@

\pagenumbering{arabic}
\setcounter{page}{1}

@@

We swept through values for $x_{\rm max.}$ within $\mathrm{2\,s} \leq x_{\rm max.} \leq \mathrm{750\,s}$, with $\rm 750 \, s$ being the maximal possible synaptic lifetime to be recorded. We estimated the power-law exponent with the aforementioned package for each value of $x_{\rm max.}$ and calculated $d_{\rm max.}$. The value of $x_{\rm max.}$ resulting in the smallest $d_{\rm max.}^{min.}$ was then picked for the final estimation of $\alpha$. We did expect $d_{\rm max.}$ to go through a minimum for a certain value of $x_{\rm max.}$ and to increase again due to the statistical deviations for long lifetimes. We did not observe this behavior, however. Instead, $d_{\rm max.}$ was monotonically decreasing but converging. Therefore, we actually found its minimal value for $x_{\rm max.} = \rm 750 \, s$ for both diffusive homeostasis and non-diffusive homeostasis ($d_{\rm max.,diff.}^{min.} = 0.30$, $d_{\rm max.,non-diff.}^{min.} = 0.34$). We thus accepted the values for $\alpha$ acquired by MLE for both entire datasets as valid, yielding $\mathrm{\alpha_{\rm diff.} = -1.455}$ and $\mathrm{\alpha_{\rm don-diff.} = -1.468}$. The resulting exponents are slightly smaller than previously reported values of $\mathrm{\approx - 5/3}$ \cite{SORN_Paper}. 

@@

\caption[Distribution of lifetimes of recurrent excitatory synaptic connections]{Distribution of lifetimes of recurrent excitatory synaptic connections. Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a power-law exponent of $\mathrm{\alpha_{\rm diff.} = -1.455}$ (standard error $\mathrm{\sigma_{\rm diff.} = 5.52 \cdot 10^{-4}}$) for diffusive homeostasis and $\mathrm{\alpha_{\rm don-diff.} = -1.468}$ (standard error $\mathrm{\sigma_{\rm don-diff.} = 5.70 \cdot 10^{-4}}$) for non-diffusive homeostasis.}

>>>>

\documentclass[10pt,a4paper]{article}
%\usepackage{layouts}
%\usepackage[a4paper,margin=1.5in]{geometry}
\usepackage{geometry}
\geometry{a4paper,lmargin=1.6969in,rmargin=1.3031in,tmargin=1.5in,bmargin=1.5in,twoside}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{tabu}
\usepackage{float}
\usepackage{upgreek}
\usepackage[titletoc,title]{appendix}
\usepackage{afterpage}
\usepackage[nottoc,notlot,notlof]{tocbibind}

@@

\pagenumbering{gobble}
\setcounter{page}{1}

@@

\pagenumbering{arabic}
\setcounter{page}{4}

@@

We swept through values for $x_{\rm max.}$ within $\mathrm{2\,s} \leq x_{\rm max.} \leq \mathrm{750\,s}$, with $\rm 750 \, s$ being the maximal possible synaptic lifetime to be recorded. We estimated the power-law exponent with the aforementioned package for each value of $x_{\rm max.}$ and calculated $d_{\rm max.}$. The value of $x_{\rm max.}$ resulting in the smallest $d_{\rm max.}^{min.}$ was then picked for the final estimation of $\alpha$. We did expect $d_{\rm max.}$ to go through a minimum for a certain value of $x_{\rm max.}$ and to increase again due to the statistical deviations for long lifetimes. We did not observe this behavior, however. Instead, $d_{\rm max.}$ was monotonically decreasing but converging. Therefore, we actually found its minimal value for $x_{\rm max.} = \rm 750 \, s$ for both diffusive homeostasis and non-diffusive homeostasis ($d_{\rm max.,diff.}^{min.} = 0.30$, $d_{\rm max.,non-diff.}^{min.} = 0.34$). We thus accepted the values for $\alpha$ acquired by MLE for both entire datasets as valid, yielding $\mathrm{\alpha_{\rm diff.} = -1.455}$ and $\mathrm{\alpha_{\rm non-diff.} = -1.468}$. The resulting exponents are slightly smaller than previously reported values of $\mathrm{\approx - 5/3}$ \cite{SORN_Paper}. 

@@

\caption[Distribution of lifetimes of recurrent excitatory synaptic connections]{Distribution of lifetimes of recurrent excitatory synaptic connections. Linear fits ignoring falloff (only using bins with $\rm t \leq 150 \, s$) for large synaptic lifetimes resulted in a power-law exponent of $\mathrm{\alpha_{\rm diff.} = -1.455}$ (standard error $\mathrm{\sigma_{\rm diff.} = 5.52 \cdot 10^{-4}}$) for diffusive homeostasis and $\mathrm{\alpha_{\rm non-diff.} = -1.468}$ (standard error $\mathrm{\sigma_{\rm non-diff.} = 5.70 \cdot 10^{-4}}$) for non-diffusive homeostasis.}
